---
title: "Boycott_China"
Authoritarianismor: "Mingmin Yang"
date: "12/2/2019"
output: pdf_document
---

```{r, include=FALSE}
library(quanteda);library(topicmodels);library(dplyr);library(tidyr);
library(broom);library(readtext);library(jiebaR);
library(jiebaRD);library(fastDummies);library(ggplot2);library(stm);library(corrplot);library(Hmisc);
library(sjPlot);library(sjmisc);library(reshape2);library(stargazer)
knitr::opts_chunk$set(echo = FALSE)

setwd("/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/")
WJX3 <- readxl::read_xlsx("SurveyData.xlsx") 
colnames(WJX3)[7] <- 'StudyAbroad'
colnames(WJX3)[9] <- 'Patriotism'
colnames(WJX3)[10] <- 'Party'
colnames(WJX3)[11] <- 'Nationalism'
colnames(WJX3)[13] <- 'Control'
WJX3$Tour <- NULL
colnames(WJX3)[5] <- "Tour"
WJX3$Boycott <- NULL
colnames(WJX3)[18] <- "Boycott"
colnames(WJX3)[7] <- "Authoritarianism"


colnames(WJX3)
WJX3_no_treatment <- readxl::read_xlsx("SurveyDataNoTreatment.xlsx")

colnames(WJX3_no_treatment)[8] <- 'StudyAbroad'
WJX3_no_treatment$...1 <- NULL
WJX3_no_treatment$Tour <- NULL
colnames(WJX3_no_treatment)[5] <- "Tour"
WJX3_no_treatment$Boycott <- NULL
colnames(WJX3_no_treatment)[11] <- "Boycott"
colnames(WJX3_no_treatment)[7] <- "Authoritarianism"

colnames(WJX3_no_treatment)

```

```{r, results='asis'}
stargazer(as.data.frame(WJX3_no_treatment), type = "latex", digits=1, flip = TRUE)
stargazer(as.data.frame(WJX3_no_treatment), type = "latex", digits=1)
```
#https://stackoverflow.com/questions/43245920/how-to-resize-tables-generated-by-stargazer-in-r-markdown

#Table 2: Heatmap
```{r}
cordata <- round(cor(WJX3_no_treatment),2)
melted_cordata <- melt(cordata) #Melt data to bring the correlation values in two axis
heatmap1 <- ggplot(data = melted_cordata, aes(x=Var1, y=Var2, fill=value, label= value)) + geom_tile() + scale_fill_gradient2(low = "#132B43",high ="#56B1F7",mid = "white") + geom_text() + theme(axis.text.x=element_text(angle = 90,vjust = 0))# + geom_label()
heatmap1

#png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/heatmap1.png")
#plot(heatmap1)
#dev.off()
```

#Figure 1: Treatment on Anti-Foreign Boycott
```{r}
WJX3_sub1 <- WJX3 %>% group_by(Treatment, as.factor(Boycott)) %>% tally()
WJX3_sub1 <- WJX3_sub1 %>% rename('Boycott'='as.factor(Boycott)','count'='n')
figure1 <- ggplot(WJX3_sub1, aes(Treatment, count, fill=Boycott)) + geom_bar(stat="identity", position=position_dodge()) + # scale_fill_grey(start=0.8, end=0.2) + 
theme_classic() + coord_flip()
figure1

#png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/figure1.png")
#plot(figure1)
#dev.off()
```


```{r}
#https://rcompanion.org/rcompanion/b_05.html
#http://www.r-tutor.com/elementary-statistics/inference-about-two-populations/comparison-two-population-proportions
#dplyr::filter(WJX3, Treatment == 'control' & Boycott == 1)
#dplyr::filter(WJX3, Treatment == 'Trt1' & Boycott == 1)
#dplyr::filter(WJX3, Treatment == 'Trt2' & Boycott == 1)
#dplyr::filter(WJX3, Treatment == 'Trt3' & Boycott == 1)
#dplyr::filter(WJX3, Treatment == 'Trt4' & Boycott == 1)
#dplyr::filter(WJX3, Treatment == 'Trt5' & Boycott == 1)

Input =("
Treatment NoBoycott Boycott
'Control'   106       131
'Trt1'      4       223
'Trt2'      200       27
'Trt3'      20       206
'Trt4'      22       207
'Trt5'      53      181
")

BoycottDifference = read.table(textConnection(Input),header=TRUE)

BoycottDifference =
  mutate(BoycottDifference,
         Sum = NoBoycott + Boycott)

table1_BoycottDifference =
  mutate(BoycottDifference,
         Prop = Boycott / Sum,
         low.ci = apply(BoycottDifference[c("Boycott", "Sum")], 1,
                        function(y) binom.test(y['Boycott'], y['Sum'])$ conf.int[1]),
         high.ci = apply(BoycottDifference[c("Boycott", "Sum")], 1,
                         function(y) binom.test(y['Boycott'], y['Sum'])$ conf.int[2])
  )

BoycottDifference <- table1_BoycottDifference
BoycottDifference
#table1_BoycottDifference
#png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/table1_BoycottDifference.png")
#plot(table1_BoycottDifference)
#dev.off()
library(gridExtra)
tableGrob(BoycottDifference)
#https://stackoverflow.com/questions/30794273/plot-a-data-frame-as-a-table/30794389
```

```{r}
### Plot (Bar chart plot)
library(ggplot2)
figure2 <- ggplot(BoycottDifference,
       aes(x=Treatment, y=Prop)) +
  geom_bar(stat="identity", fill="gray40",
           colour="black", size=0.5,
           width=0.7) +
  geom_errorbar(aes(ymax=high.ci, ymin=low.ci),
                width=0.2, size=0.5, color="black") +
  xlab("Treatment") +
  ylab("Boycott by Treatment") +
  scale_x_discrete(labels=c("Control", "Trt1",
                            "Trt2","Trt3","Trt4","Trt5")) +
  ## ggtitle("Main title") +
  theme(axis.title=element_text(size=14, color="black",
                                face="bold", vjust=3)) +
  theme(axis.text = element_text(size=12, color = "gray25",
                                 face="bold")) +
  theme(axis.title.y = element_text(vjust= 1.8)) +
  theme(axis.title.x = element_text(vjust= -0.5))

figure2

png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/figure2.png")
plot(figure2)
dev.off()
```

## Model 1
```{r}
model1 <- glm(Boycott ~ Trt1 + Trt2 + Trt3 + Trt4 + Trt5 + Nationalism + Patriotism + Authoritarianism + Tour + StudyAbroad + Age + Education + Gender + Race + Income + Party, data=WJX3, family = "binomial")

```

```{r}
plot_model1 <- plot_model(model1, type = "pred", terms = c("Nationalism ","Trt1"))
plot_model2 <- plot_model(model1, type = "pred", terms = c("Nationalism ","Trt2"))
plot_model3 <- plot_model(model1, type = "pred", terms = c("Nationalism ","Trt3"))
plot_model4 <- plot_model(model1, type = "pred", terms = c("Nationalism ","Trt4"))
plot_model5 <- plot_model(model1, type = "pred", terms = c("Nationalism ","Trt5"))
#https://strengejacke.github.io/sjPlot/articles/plot_interactions.html
#https://cran.r-project.org/web/packages/sjPlot/vignettes/plot_model_estimates.html
png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/plot_model1.png")
plot(plot_model1)
dev.off()
png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/plot_model2.png")
plot(plot_model2)
dev.off()
png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/plot_model3.png")
plot(plot_model3)
dev.off()
png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/plot_model4.png")
plot(plot_model4)
dev.off()
png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/plot_model5.png")
plot(plot_model5)
dev.off()


```

```{r}
WJX3_1 <- WJX3
WJX3_1$Treatment <- to_factor(WJX3_1$Treatment)
model1_1 <- glm(Boycott ~ Treatment  + Trt1 + Trt2 + Trt3 + Trt4 + Trt5 + Nationalism + Patriotism + Authoritarianism + Tour + StudyAbroad + Age + Education + Gender + Race + Income + Party, data=WJX3_1, family = "binomial")
plot_model6 <- plot_model(model1_1, type = "pred", terms = c("Nationalism ","Treatment"), grid = TRUE)
#png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/plot_model6.png")
#plot(plot_model6)
#dev.off()
```
#https://cran.r-project.org/web/packages/sjPlot/vignettes/plot_interactions.html
```


# Model 2, Nationalism
```{r}
model2 <- glm(Boycott ~ Trt1 + Trt2 + Trt3 + Trt4 + Trt5 + Nationalism + Patriotism + Authoritarianism + Tour + StudyAbroad + Age + Education + Gender + Race + Income + Party + Trt1*Nationalism + Trt2*Nationalism + Trt3*Nationalism + Trt4*Nationalism +Trt5*Nationalism, data=WJX3, family = "binomial")

model2_1 <- glm(Boycott ~ Trt1 + Trt2 + Trt3 + Trt4 + Trt5 + Nationalism + Patriotism + Authoritarianism + Tour + StudyAbroad + Age + Education + Gender + Race + Income + Party + Treatment*Nationalism,data=WJX3 , family = "binomial")

plot_model7 <- plot_model(model2, type = "pred", terms = c("Nationalism","Trt1"), grid = TRUE)
plot_model8 <- plot_model(model2_1, type = "pred", terms = c("Nationalism","Treatment"), grid = TRUE)

#png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/plot_model7.png")
#plot(plot_model1)
#dev.off()
#png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/plot_model8.png")
#plot(plot_model2)
#dev.off()
```

# Model 3, Patriotism
```{r}
model3 <- glm(Boycott ~ Trt1 + Trt2 + Trt3 + Trt4 + Trt5 + Nationalism + Patriotism + Authoritarianism + Tour + StudyAbroad + Age + Education + Gender + Race + Income + Party + Trt1*Patriotism + Trt2*Patriotism + Trt3*Patriotism + Trt4*Patriotism +Trt5*Patriotism, data=WJX3, family = "binomial")

model3_1 <- glm(Boycott ~ Trt1 + Trt2 + Trt3 + Trt4 + Trt5 + Nationalism + Patriotism + Authoritarianism + Tour + StudyAbroad + Age + Education + Gender + Race + Income + Party + Treatment*Patriotism,data=WJX3 , family = "binomial")

pplot_model9 <- plot_model(model3, type = "pred", terms = c("Patriotism","Trt1"), grid = TRUE)
pplot_model10 <- plot_model(model3_1, type = "pred", terms = c("Patriotism","Treatment"), grid = TRUE)

png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/plot_model9.png")
plot(plot_model1)
dev.off()
#png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/plot_model10.png")
#plot(plot_model2)
#dev.off()
```

# Model 4, interact with Income
```{r}
model4 <- glm(Boycott ~ Trt1 + Trt2 + Trt3 + Trt4 + Trt5 + Nationalism + Patriotism + Authoritarianism + Tour + StudyAbroad + Age + Education + Gender + Race + Income + Party + Trt1*Income + Trt2*Income + Trt3*Income + Trt4*Income +Trt5*Income,data=WJX3 , family = "binomial")
#summary(model4)
model4_1 <- glm(Boycott ~ Trt1 + Trt2 + Trt3 + Trt4 + Trt5 + Nationalism + Patriotism + Authoritarianism + Tour + StudyAbroad + Age + Education + Gender + Race + Income + Party + Treatment*Income,data=WJX3 , family = "binomial")

plot_model10 <- plot_model(model4_1, type = "pred", terms = c("Income","Trt1"), grid = TRUE)

#png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/plot_model10.png")
#plot(plot_model10)
#dev.off()
```

# Model 5, interact with Age
```{r}
model5 <- glm(Boycott ~ Trt1 + Trt2 + Trt3 + Trt4 + Trt5 + Nationalism + Patriotism + Authoritarianism + Tour + StudyAbroad + Age + Education + Gender + Race + Income + Party + Trt1*Age + Trt2*Age + Trt3*Age + Trt4*Age +Trt5*Age,data=WJX3 , family = "binomial")

model5_1 <- glm(Boycott ~ Trt1 + Trt2 + Trt3 + Trt4 + Trt5 + Nationalism + Patriotism + Authoritarianism + Tour + StudyAbroad + Age + Education + Gender + Race + Income + Party + Treatment*Age,data=WJX3 , family = "binomial")

plot_model(model5, type = "pred", terms = c("Age","Trt1"), grid = TRUE)

plot_model11 <- plot_model(model5_1, type = "pred", terms = c("Age","Treatment"), grid = TRUE)

#png(filename="/Users/ming-minyang/Desktop/Poli-psch/Survey/WJX2/plot_model11.png")
#plot(plot_model11)
#dev.off()
```

```{r, results='asis'}
stargazer::stargazer(model1, model2, model3, type = 'latex', single.row=TRUE)
stargazer::stargazer(model1, model2, model3, model4, model5, type = 'latex', single.row=TRUE)
```

# Entropy balancing
Entropy balancing
```{r}
WJX3_entrophy2 <- readxl::read_xlsx("WJX3_entrophy2.xlsx")
WJX3_entrophy2$...1 <- NULL
treatment_en <- WJX3_entrophy2$Treatment_entropy
WJX3_entrophy2$Treatment_entropy <- NULL #Remove the 'control (real data)' and 'treatment (real China's demography)'.
treatment_assign <- WJX3_entrophy2$Treatment 
WJX3_entrophy2$Treatment <- NULL 
```

```{r}
library(ebal)
eb.out <- ebalance(Treatment=treatment_en, X=WJX3_entrophy2)
```

```{r}
#means in treatment group data 
apply(WJX3_entrophy2[treatment_en==1,],2,mean)
# means in reweighted control group data / 
apply(WJX3_entrophy2[treatment_en==0,],2,weighted.mean,w=eb.out$w)
# means in raw data control group data
apply(WJX3_entrophy2[treatment_en==0,],2,mean)
```

Trim weights
```{r}
eb.out.tr <- ebalance.trim(eb.out)
```

```{r}
# means in reweighted control group data
apply(WJX3_entrophy2[treatment_en==0,],2,weighted.mean,w=eb.out.tr$w)
apply(WJX3_entrophy2[treatment_en==1,],2,mean)

# untrimmed and trimmed weights
round(summary(eb.out$w),2)
round(summary(eb.out.tr$w),2)
```

```{r}
model6 <- glm(Boycott ~ Treatment  + Nationalism + Patriotism + Age + Education + Gender  + Race + Income + Party + Tour
            , data=WJX3, family = "binomial")

model7 <- glm(Boycott ~ Treatment  + Nationalism + Patriotism + Age + Education + Gender  + Race + Income + Party + Tour
            , data=WJX3, weights=eb.out.tr$w, family = "binomial")
```

```{r, results='asis'}
stargazer::stargazer(model6, model7, type = 'latex', single.row=TRUE)
```





